Supplementary Material \\ \large{Heterogenous firing responses leads to diverse coupling to presynaptic activity in a simplified morphological model of layer V pyramidal neurons}

### 2016-06-20 derivation_supplementary/supplementary.tex
finished with the supplementary derivation

\begin{equation}
\left\{
\begin{split}
& g_{e0}^p = \pi \, d \, \mathcal{D}_e \, \nu_e^p \, \tau_e^p \, Q_e^p \quad ;  \quad
g_{i0}^p = \pi \, d \, \mathcal{D}_i \, \nu_i^p \, \tau_i^p \, Q_i^p \\
& g_{e0}^d = \pi \, d \, \mathcal{D}_e  \, \nu_e^d \, \tau_e^d \, Q_e^d \quad ; \quad 
g_{i0}^d = \pi \, d \, \mathcal{D}_i \, \nu_i^d \, \tau_i^d \, Q_i^d
\end{split}
\right.
\end{equation}

@@

\begin{equation}
\label{eq:x-rescale}
 X(x) = \int_0^x \frac{dx}{\lambda(x)}
\end{equation}

@@

\begin{equation}
\left\{
\begin{split}
& \mu_v(X) = v_0^p + A \, \cosh(X) + C \, \sinh(X) \quad \forall \, X \in [0,L_p] \\
& \mu_v(X) = v_0^d + B \, \cosh(X-L) + D \, \sinh(X-L) \quad \forall \, X \in [L_pL]
\end{split}
\right.
\end{equation}

@@

\item PSP at the soma
\label{sec-3-0-0-3}

The main text writes a solution for the PSP at soma of the form:

\begin{equation}
\hat{\delta v}(X=0, X_{src}, f) = K_f(X_{src}) \, 
\big(\mu_v(X_{src})-E_{rev}\big) \,  \hat{g(f)} 
\end{equation}

The correspondance with the previous calculus is to take a unitary
current \(I_f=1\) and \( K_f(X_{src}) \) given by:

@@

@@

This can be obtained from shotnoise theory \cite{Daley2007} (see also
\citetext{ElBoustani2009a} for an application similar to ours), the
general form can be expressed as:

\begin{equation}
\label{eq:vm-pwd}
P_V(f)  = \sum_{\{syn\}} N_{syn} \,  F_\mathrm{synch} \, \nu_{syn}
\, \| \hat{\mathrm{PSP}_{syn}}(f) \|^2 
\end{split}
\end{equation}

where $\{syn\}$ is the set of identical synapses, each having
$N_{syn}$ synapses, a Poisson release probability: $\nu_{syn}$ and
creating a post-synaptic event $\mathrm{PSP}_{syn}(t)$.

In addition, we added a synchrony factor $F_\mathrm{synch}$ that
accounts for the effects of the synchronous arrivals of presynaptic
events. Given the synchrony generator considered in the main text, the
synchrony factor takes the form:

@@

\section{Deriving the fluctuations properties}
\label{sec-5}

@@

>>>>

\begin{equation}
\left\{
\begin{split}
& g_{e0}^p = \pi \, d \, \mathcal{D}_e \, \nu_e^p \, \tau_e^p \, Q_e^p \quad ;  \quad
g_{i0}^p = \pi \, d \, \mathcal{D}_i \, \nu_i^p \, \tau_i^p \, Q_i^p \\
& g_{e0}^d = \pi \, d \, \mathcal{D}_e  \, \nu_e^d \, \tau_e^d \, Q_e^d \quad ; \quad 
g_{i0}^d = \pi \, d \, \mathcal{D}_i \, \nu_i^d \, \tau_i^d \, Q_i^d
\end{split}
\right.
\label{eq:1}
\end{equation}

@@

\begin{equation}
 X(x) = \int_0^x \frac{dx}{\lambda(x)}
\label{eq:x-rescale}
\end{equation}

@@

\begin{equation}
\left\{
\begin{split}
& \mu_v(X) = v_0^p + A \, \cosh(X) + C \, \sinh(X) \quad \forall \, X \in [0,L_p] \\
& \mu_v(X) = v_0^d + B \, \cosh(X-L) + D \, \sinh(X-L) \quad \forall \, X \in [L_pL]
\end{split}
\right.
\label{eq:muV-final}
\end{equation}

@@

From this calculus, we can write the PSP at the soma on the form:

\begin{equation}
\label{eq:delta-v-final}
\hat{\delta v}(X=0, X_{src}, f) = K_f(X_{src}) \, 
\big(\mu_v(X_{src})-E_{rev}\big) \,  \hat{g(f)} 
\end{equation}

where \( K_f(X_{src}) \) given by:

@@

This is obtained by taking a unitary current \(I_f=1\) in the previous calculus.

@@

This can be obtained from shotnoise theory \cite{Daley2007} (see also
\citetext{ElBoustani2009a} for an application similar to ours), the
general form of the power spectrum density can be expressed as:

\begin{equation}
P_V(f)  = \sum_{\{syn\}} N_{syn} \,  F_\mathrm{synch} \, \nu_{syn}
\, \| \hat{\mathrm{PSP}_{syn}}(f) \|^2 
\end{split}
\label{eq:vm-pwd}
\end{equation}

where $\{syn\}$ is the set of identical synapses, each having
$N_{syn}$ synapses, a Poisson release probability: $\nu_{syn}$ and
creating a post-synaptic event $\mathrm{PSP}_{syn}(t)$. In addition,
$F_\mathrm{synch}$ is a synchrony factor (depending on the variable
$s$ in the model), it accounts for the effects of the synchronous
arrivals of presynaptic events. Given the synchrony generator
considered in the main text, the synchrony factor takes the form:

@@

Now obtaining the power spectrum density $P_V(f)$ in our situation
requires to explicit the sum over synapses: $\sum_{\{syn\}}$, In our
cases, we need to sum over 1) their type (excitatory/inhibitory,
$\sum_{s \in \{e,i\}}$ ), 2) their location (we will integrate over
the dendritic length $\int_0^L dx$) 3) branches.

\begin{equation}
\begin{split}
  P_V(f)  = & \sum_{s \in \{e,i\}} \int_0^L \, dx \,  \pi \, \mathcal{D}_s
  \Big( d_t \, 2^{- \frac{2}{3} \, \lfloor \frac{B \, x}{l} \rfloor} \Big)
  \, \,  2^{\lfloor \frac{B \, x}{l} \rfloor} \, \, \,  F_\mathrm{synch} \, \nu_{s}(x)
  \, \| \hat{\delta v}_{s}(0, x, f) \|^2 \\
  & + \pi \, \mathcal{D}_i \, l_{S} \, d_{S} \, \,  F_\mathrm{synch} \, \nu_{i}(0)
  \, \| \hat{\delta v}_{i}(0, 0, f) \|^2 
\end{split}
\label{eq:vm-pwd-final}
\end{equation}

where $ \hat{\delta v}_{s}(0, x, f)$ is given by
Eq. \ref{eq:delta-v-final} (note that the dependency on synaptic type
$s$ comes from the reversal potential term $E_{rev}$ in
Eq. \ref{eq:delta-v-final}). The factor $2^{\lfloor \frac{B \, x}{l}
  \rfloor}$ corresponds to the sum of the synapses over the different
branches at the distance $x$. The term $\big( d_t \, 2^{- \frac{2}{3}
  \, \lfloor \frac{B \, x}{l} \rfloor} \Big)$ is the diameter of the
branches at the distance $x$.

The last term in Eq. \ref{eq:vm-pwd-final} corresponds to the
contribution of somatic inhibitory synapses (number of somatic
inhibitory synapses: $\pi \, \mathcal{D}_i \, l_{S} \, d_{S}$.

\section{Deriving the fluctuations properties ($\mu_V, \sigma_V, \tau_V$)}
\label{sec-5}

The final expressions for the fluctuation propeorties as a function of
($\nu_e^p, \nu_i^p, \nu_e^d, \nu_i^d, s$) are thus given by:

\begin{itemize}

  \item $\mu_V$: we obtain the mean of the fluctuations at the soma by
    taking $\mu_V(0)$ in Equation \ref{eq:muV-final}.

  \item $\sigma_V$: we obtain the standard deviation of the fluctuations from the power spectrum density in Equation \ref{eq:vm-pwd-final} and the expression:

    This integral expression was discretized and evaluated numerically

  \item $\tau_V$: we obtain the autocorrelation time of the
    fluctuations from the power spectrum density in Equation
    \ref{eq:vm-pwd-final} and the expression \cite{Zerlaut2016}:

@@

    This integral expression was discretized and evaluated numerically

\end{itemize}
